\section{Description}

In this proposal, we are aiming to describe some of the high level design for our CS4347 Machine Learning Project. For our project, we will observe the relationship between our target parameter, the value of a given home in each ZIP Code,from the given input parameters that we collect data on. Our project will focus on creating the regression algorithm needed to calculate house valuations in a ZIP Code geographical area. The project is aimed at possibly using two different regressions in order to determine the cost of a house in a given ZIP Code. One regression will take in the parameters of the house that will calculate the houses value based on the number of bedrooms, number of bathrooms, square footage, if it has a pool, if it has a garage, etc. From this regression, we will get the price of a house very generally, and then apply this price to a second regression for determining the price of this house in constraints to a specific ZIP Code. The ZIP Code will take the houses market value, but adjust this value based on the population of the ZIP Code, the number of schools in the ZIP Code, the square acreage of the ZIP Code, the average income of the ZIP Code, or any other parameters that we can find. Our analysis and application will feature all the typical parameters that are used in housing cost analysis, yet will also be more centered toward understanding how ZIP Codes can effect these trends and allow the user to have a better understanding of housing prices as a result of varying ZIP Codes. 